### 2019-10-12 ch1_introduction/content.tex
update

Over the past five years, already 450 new tools for analysing single-cell omics data have been developed\cite{zappia_exploringsinglecellrnaseq_2018}. These tools typically fall within one of nine categories (Figure \ref{fig:comp_tools}). We discuss each category in the following subsections.
Whole-genome profiling at a single-cell level harbours exceptional opportunities to discover new aspects of biology and redefine existing knowledge.

\begin{figure}[htb!]
	\centering
	\includegraphics[width=.75\linewidth]{fig/comptools/comptools_3.pdf} 
	\caption{
		\textbf{Computational tools developed for processing single-cell omics data usually lie within one of nine categories.}
		\textbf{A:} Normalisation, separating meaningful biological signal from technical noise or irrelevant biological information.
		\textbf{B:} Data imputation, masking dropouts.
		\textbf{C:} Data integration, combining multiple single-cell modalities.
		\textbf{D:} Dimensionality reduction, providing a visual overview of the main cellular heterogeneity in the dataset.
		\textbf{E:} Clustering, grouping together similar cells.
		\textbf{F:} Trajectory inference, identifying and characterising transitions between different cellular states.
		\textbf{G:} Network inference, predicting gene regulatory interactions from cell-to-cell heterogeneity.
		\textbf{H:} RNA velocity, inferring the directionality of trajectories by predicting the future state of each cell.
		\textbf{I:} Trajectory alignment, aligning multiple trajectories.
	}
	\label{fig:comp_tools}
\end{figure}

\subsection{Normalisation}

\subsection{Data imputation}

\subsection{Data integration}

@@

\mycomment{This section is not very interestingly written}

@@

\mycomment{Could still expand this section with pieces from the EJI paper, though it needs to be adapted strongly.}

>>>>

Over the past five years, already 450 new tools for analysing single-cell omics data have been developed\cite{zappia_exploringsinglecellrnaseq_2018}. These tools typically fall within one of seven categories (Figure \ref{fig:comp_tools}). We discuss each category in the following subsections.
Whole-genome profiling at a single-cell level harbours exceptional opportunities to discover new aspects of biology and redefine existing knowledge.

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\linewidth]{fig/comptools/comptools_4.pdf} 
	\caption{
		\textbf{Computational tools developed for processing single-cell omics data usually lie within one of seven categories.}
		\textbf{A:} Example of a count matrix from a scRNA-seq dataset, showing only 100 genes (rows) and 100 cells (columns).
		\textbf{B:} Dimensionality reduction, providing a visual overview of the main cellular heterogeneity in the dataset.
		\textbf{C:} Clustering, grouping together cells with similar omics profiles.
		\textbf{D:} Trajectory inference, identifying and characterising transitions between different cellular states.
		\textbf{E:} Differential expression, \ldots.
		\textbf{F:} Network inference, predicting gene regulatory interactions from cell-to-cell heterogeneity.
		\textbf{G:} RNA velocity, inferring the directionality of trajectories by predicting the future state of each cell.
		\textbf{H:} Trajectory alignment, aligning multiple trajectories.
	}
	\label{fig:comp_tools}
\end{figure}

@@

@@

\mycomment{Could still expand this section with pieces from the EJI paper, though it needs to be adapted strongly.}
\subsection{Differential expression}
